quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-31 paper-quollr.Rmd
Added citation for tripack

The `tri_bin_centroids()` function generates a triangulation object from the x and y coordinates of hexagon centroids using the `tripack::tri.mesh()` function. This triangulation forms the structural basis for identifying adjacent bins.

>>>>

The `tri_bin_centroids()` function generates a triangulation object from the x and y coordinates of hexagon centroids using the `tripack::tri.mesh()` function (@albrecht2025). This triangulation forms the structural basis for identifying adjacent bins.
